Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-09 Model.tex
More notation fiddling

Formally then, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=P_{s, s_{w}, \theta_{m}} + P_{h, \theta_{w}, s_{m}} + P_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h), p_{m}(l, m, h)\).

\begin{table}
\center
\subfloat[Social cost, \(P_{s}\)\label{tab:Social-cost-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

@@

\subfloat[Health outcome, \(P_{h}\)\label{tab:Referral-payoff-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

@@

\subfloat[Referral cost, \(P_{c}\)\label{tab:inst_cost_matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9, 0 & -9, 0 & -9, 0\tabularnewline
\cline{2-5} 
 & Don't refer & 0, 0 & 0, 0 & 0, 0\tabularnewline
\hline 
\end{tabular}

@@

Where \(n_{j}\) is simply the count of occurrences of pair \(j\), so
that the belief that a signal \(j\) the number
of times that type has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.

As before, midwives follow a similar pattern but per signal.

@@

The second Bayesian agent augments the reasoning of the simple payoff model, approximating \(u_{w}\) with a more complex function - \(f(s_{w}, \theta_{w}, \sigma_{s}, \sigma_{r})=g(s_{w}, \theta_{w}, \sigma_{s}) + h(s_{w}, \theta_{w}, \sigma_{r})\). For women, this means that they maintain two sets of beliefs: a Dirichlet mixture which represents the believed distribution of midwife types, and a second set linking signals to referrals.

Formally, let \(D=\{D_{h}, D_{s}\}\), \(\alpha=\{\alpha_{h},\alpha_{s}\}\), and \(n=\{n_{h},n_{s}\}\). The quantity to be minimised then becomes -

\begin{equation}
R(i)= \sum_{z=1}\sum_{j=1}-P_{w, i, z, j}P(x=l|D_{s},\alpha_{s})P(x=j|D_{h},\alpha_{h})\label{eq:risk}
\end{equation}

So that the risk of a signal, \(i\) is the sum of all possible payoffs multiplied by the probability of that payoff occurring.

@@

\begin{equation}
R(i, j)= \sum_{z=1}\sum_{j=1}-P_{m, i, z, j}P(x=l|D_{s},\alpha_{s})P(x=j|D_{h},\alpha_{h})\label{eq:mw_risk}
\end{equation}

>>>>

Formally then, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h), p_{m}(l, m, h)\).

\begin{table}
\center
\subfloat[Social cost, \(X_{s}\)\label{tab:Social-cost-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

@@

\subfloat[Health outcome, \(X_{h}\)\label{tab:Referral-payoff-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

@@

\subfloat[Referral cost, \(X_{c}\)\label{tab:inst_cost_matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9, 0 & -9, 0 & -9, 0\tabularnewline
\cline{2-5} 
 & Don't refer & 0, 0 & 0, 0 & 0, 0\tabularnewline
\hline 
\end{tabular}

@@

Where \(n_{j}\) is simply the count of occurrences of pair \(j\), so
that the belief that a signal \(j\) the number
of times that type has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.
As before, midwives follow a similar pattern but per signal.

\begin{equation}
R_{w}(s_{w}) = \sum_{x\in \Theta} -xp(x | s_{w})
\end{equation}
\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{x\in \Theta} -xp(x | s_{w}\wedge s_{m})
\end{equation}

@@

The second Bayesian agent augments the reasoning of the simple payoff model, approximating \(u_{w}\) with a more complex function - \(f(s_{w}, \theta_{w}, \sigma_{s}, \sigma_{r})=g(s_{w}, \theta_{w}, \sigma_{s}) + h(s_{w}, \theta_{w}, \sigma_{r})\). Women maintain two sets of beliefs, one each for \(g\) and \(h\), corresponding respectively to \(p_{m}\), and the probability of referral. This leads to the risk function -

\begin{equation}
R(s_{w}) = \sum_{i\in s_{m}}\sum_{j\in \theta_{m}} -u_{w}(s_{w}, s_{m, i}, \theta_{w}, \theta_{m, j})p(j)p(i | s_{w})
\end{equation}

So that the risk of a signal is the sum of the products of all payoffs with the probabilities of their entailed midwife types and responses.

@@

\begin{equation}
R(s_{w}, s_{m}) = \sum_{i\in \theta_{w}} -u_{w}(s_{w}, s_{m}, \theta_{w, i}, \theta_{m})p(i | s_{w})
\end{equation}
